---
title: "My answers"
author: "My name"
date: "17 Oct 2022"
output: html_document
---

```{r setup, include = FALSE}
library(tidyverse)
```

### Judgment - part one

This short tutorial will allow you to explore `dplyr` functionality based on the previous lecture. Every question can be answered with a combination of `%>%` pipes. You should refrain from using temporary variables and statements outside of the range of the tidyverse.

The first part does not require joins or pivots.

##### Import the [data from the website](https://biostat2.uni.lu/practicals/data/judgments.tsv).

Assign to the name `judgments`

```{r}
# Write your answer here
```

##### Use `glimpse()` to identify columns and column types.

##### Select all columns that refer to the STAI questionnaire

```{r}
# Write your answer here
```

##### Select all subjects older than 25

```{r}
# Write your answer here
```

##### Retrieve all subjects younger than 20 which are in the stress group

The column for the group is `condition`.

```{r}
# Write your answer here
```

##### Abbreviate the gender column such that only the first character remains.
Create a new column in the process.

```{r}
# Write your answer here
```

##### Normalize the values in the REI group

Divide all entries in the REI questionnaire by 5, the maximal value.

```{r}
# Write your answer here
```

##### Find the moral dilemma with the highest average score across all participants.

```{r}
# Write your answer here
```

##### Identify the highest score and the lowest sum of REI scorees per participant.
Your result should be a single tible with one row and two columns.

Hint: You need to consider that some parts of the calculations have to done per participant, others are summarising for the complete data set.
```{r}
# Write your answer here
```

##### Find the *moral dilemma* with the highest average score and the highest median score across all participants.
Compute the median and the mean.

```{r}
# Write your answer here
```

